Simple repression draft

### 2020-05-21 doc/appendix_03_regulated_promoters.tex
Added to constit prom Bayesian inference + minor file reorg

% !TEX root = ./busty_transcription.tex
\section{Generating function solution for bursty promoters}

@@

>>>>

% !TEX root = ./busty_transcription.tex
\section{Bursty promoter models - generating function solutions and numerics}
\label{sec:gen_fcn_appdx}

@@

Now we may recover the mRNA probability distribution of interest
by differentiating the generating function, or by consulting a
standard reference\mmnote{maybe van Kampen, check},
from which we find that
\begin{equation}
p(m) = \frac{\Gamma(m+\lambda)}{\Gamma(m+1)\Gamma(\lambda)}
        \theta^\lambda (1-\theta)^m.
\end{equation}
Note that the ratio of gamma functions is often expressed as a
binomial coefficient, but since $\lambda$ may be non-integer,
this would be ill-defined.
Re-expressing this exclusively in our variables of interest,
burst rate $\lambda$ and mean burst size $b$, we have
\begin{equation}
p(m) = \frac{\Gamma(m+\lambda)}{\Gamma(m+1)\Gamma(\lambda)}
        \left(\frac{1}{1+b}\right)^\lambda
        \left(\frac{b}{1+b}\right)^m.
\label{eq:nbinom_deriv_final}
\end{equation}
